---
title: "W2_R"
output:
  html_document: default
  pdf_document: default
---

load the R package

```{r}
rm(list = ls())

library(readr)
library(dplyr)
```

## Question 2

### #1. load data

```{r}
data <- read_csv("econmath.csv")
data <- na.omit(data)
```

### #2. check the head of the table

```{r}
head(data)
```

### #3. find the min of variable "acteng", "actmth" and "colgpa".

```{r}
min(data$acteng)
min(data$actmth)
min(data$colgpa)
min(data$score)
```

### #4. find the max

```{r}
max(data$acteng)
max(data$actmth)
max(data$colgpa)
max(data$score)
```

### #5. find the mean

```{r}
mean(data$acteng)
mean(data$actmth)
mean(data$colgpa)
mean(data$score)
```

### #6. find the sd

```{r}
sd(data$acteng)
sd(data$actmth)
sd(data$colgpa)
sd(data$score)
```

### #7. estimate the OLS model: $$score = \beta_0 + \beta_1 \cdot colgpa + \beta_2 \cdot actmth + \beta_3 \cdot acteng + u$$
```{r}
OLS1 = lm(score ~ colgpa + actmth + acteng , data=data)

summary(OLS1)
```

### #8. standardize all variables and re-estimate the OLS model: $$score = \beta_0 + \beta_1 \cdot colgpa + \beta_2 \cdot actmth + \beta_3 \cdot acteng + u$$
```{r}

data_st = select(data, score, colgpa, actmth, acteng )

data_st$score  = (data_st$score  - mean(data_st$score ))/sd(data_st$score )
data_st$colgpa = (data_st$colgpa - mean(data_st$colgpa))/sd(data_st$colgpa)
data_st$actmth = (data_st$actmth - mean(data_st$actmth))/sd(data_st$actmth)
data_st$acteng = (data_st$acteng - mean(data_st$acteng))/sd(data_st$acteng)

OLS2 = lm(score ~ colgpa + actmth + acteng , data=data_st)

summary(OLS2)
```

## Question 3

### #1. load data

```{r}
data <- read_csv("hprice1.csv")
data <- na.omit(data)
```

### #2. check the head of the table

```{r}
head(data)
```

### #3. find the min of variable "price", "sqrmtr", "lotsize" and 'bdrms'.

```{r}
min(data$price)
min(data$sqrft)
min(data$bdrms)
```

### #4. find the max

```{r}
max(data$price)
max(data$sqrfg)
max(data$bdrms)
```

### #5. find the mean

```{r}
mean(data$price)
mean(data$sqrft)
mean(data$bdrms)
```

### #6. find the mean

```{r}
sd(data$price)
sd(data$sqrft)
sd(data$bdrms)
```

### #7. estimate the OLS model: $$price = \beta_0 + \beta_1 \cdot sqrmtr + \beta_2 \cdot lotsize + \beta_3 \cdot bdrms + u$$
```{r}
OLS1 = lm(price ~ sqrft + bdrms , data=data)

summary(OLS1)
```

### #8. standardize all variables and re-estimate the OLS model
```{r}

data_st = select(data, price, sqrft, bdrms)

data_st$price = (data_st$price - mean(data_st$price))/sd(data_st$price)
data_st$sqrft = (data_st$sqrft - mean(data_st$sqrft))/sd(data_st$sqrft)
data_st$bdrms = (data_st$bdrms - mean(data_st$bdrms))/sd(data_st$bdrms)

OLS2 = lm(price ~ sqrft + bdrms , data=data_st)

summary(OLS2)
```

### #9. predict the value of the house
```{r}

new_obs <- data.frame( sqrft = 2438, bdrms = 4)
predict(OLS1, new_obs)

```

### #10. compute the prediction residual if price = 300
```{r}

new_obs <- data.frame( price = 300, sqrft = 2438,  bdrms = 4)
300 - predict(OLS1, new_obs)

```
